???Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry

### 2023-08-21 article.tex
minor changes

%% \title{Title\tnoteref{label1}}
\title{Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry}
% Regional differences in Australian winegrowing (Quality)?

@@

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
\begin{highlights}
  \item Comparative analysis of resource use, quality and quantity in Australian winegrowing.
  \item Regional comparison of outcomes and resource use in Australian winegrowing regions.
  \item Baseline models for comparing wine crops.
  \item Analysis of national, decade long data source.
\end{highlights}
\end{frontmatter}

@@

We examine the similarity between these classifications and the variables that are significant in classifying profitable vs not.
How do regional changes affect that. What is similar and and what is different.

We can link these contributing factors back to the baselines - at least anaecdotally, or in an unpublished section. THis will be good for the thesis.

>>>>

%% \title{Title\tnoteref{label1}}
\title{???Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry}
% Regional differences in Australian winegrowing (Quality)?

@@

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
\begin{highlights}
  \item ???
  \item ???
  \item ????
  \item ????
\end{highlights}
\end{frontmatter}

@@

We examine the similarity between these classifications and the variables that are significant in classifying profitable vs not.
How do regional changes affect that. What is similar and what is different.

We can link these contributing factors back to the baselines - at least anecdotally, or in an unpublished section. This will be good for the thesis.
